\documentclass[a4paper,11pt]{article}
\usepackage[british]{babel}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\usepackage{multirow}
\usepackage{caption}
\usepackage{tikz,pgfplots}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\title{\textbf{Low-level Parallel Programming (course 1DL550) \\
    Uppsala University -- Spring 2015 \\
    Report for Lab 2 by Team 14}}
\author{Fredrik Larsson \and Jimmy Holm \and Per Bergqwist}
\date{\today}
\begin{document}
\maketitle
\section{System specification}
The CPU of the system used for gathering the data presented was an
Intel i7 2600k running at a frequency of 4GHz. The system was able to
use four cores with Hyper-threading enabled, meaning a possibility of
using eight logical cores simultaneously with the drawback that the
performance gain from using more than four cores varies depending on
the tasks. To collect the data for OpenCL an AMD HD7970 GPU with 3GB
of memory was used running with the standard clock of 925MHz.
\section{Plot}
\begin{center}
  \begin{figure}[h]
    \pgfplotsset{grid style={dotted,gray}}
    \begin{tikzpicture}
      \begin{axis}[
          width=0.8\textwidth,
          height=0.6\textwidth,
          xtick={1,...,8},
          xmin=1,
          xmax=8,
          ymin=0,
          ymax=1.4,
          grid=both,
          legend style={at={(1.35,1)},anchor=north east},
          legend entries={
            \footnotesize{PThreads},
            \footnotesize{PThreads SIMD},
            \footnotesize{OpenMP},
            \footnotesize{OpenMP SIMD},
            \footnotesize{OpenCL},
            \footnotesize{Sequential SIMD},
            \footnotesize{Sequential}
          },
          xlabel={\small Number of threads},
          ylabel={\small Time (Fraction of sequential time)}
        ]
        %% pthreads
        \addplot[color=orange,mark=square*] coordinates{
          (1,1.13478)
          (2,0.675423)
          (3,0.541)
          (4,0.537409)
          (5,0.870581)
          (6,0.998571)
          (7,1.16046)
          (8,1.44631)
        };
        %% pthreads simd
        \addplot[color=teal,mark=square*] coordinates{
          (1,0.850037)
          (2,0.528359)
          (3,0.449847)
          (4,0.461004)
          (5,0.625313)
          (6,0.820093)
          (7,1.12675)
          (8,1.38598)
        };
        %% omp
        \addplot[densely dashed,color=orange,mark=*] coordinates{
          (1,0.995768)
          (2,0.505261)
          (3,0.3461)
          (4,0.278532)
          (5,0.291689)
          (6,0.250976)
          (7,0.230638)
          (8,0.24856)
        };
        %% omp simd
        \addplot[densely dashed,color=teal,mark=*] coordinates{
          (1,0.731386)
          (2,0.375731)
          (3,0.257043)
          (4,0.207856)
          (5,0.239281)
          (6,0.206265)
          (7,0.198881)
          (8,0.193466)
        };
        %% opencl
        \addplot[color=teal,mark=x] coordinates{
          (1,0.929541)
          (2,0.929541)
          (3,0.929541)
          (4,0.929541)
          (5,0.929541)
          (6,0.929541)
          (7,0.929541)
          (8,0.929541)
        };
        %% simd
        \addplot[color=purple,mark=x] coordinates{
          (1,0.721943)
          (2,0.721943)
          (3,0.721943)
          (4,0.721943)
          (5,0.721943)
          (6,0.721943)
          (7,0.721943)
          (8,0.721943)
        };
        \addplot[color=orange,mark=x] coordinates{
          (1,1)
          (2,1)
          (3,1)
          (4,1)
          (5,1)
          (6,1)
          (7,1)
          (8,1)
        };
        %% \draw (axis cs:2,0.944114) -- (axis cs:14,0.944114);
        %% \draw (axis cs:2,0.722371) -- (axis cs:14,0.722371);
      \end{axis}
    \end{tikzpicture}
    \caption{Normal scenario}
  \end{figure}
\end{center}
\begin{center}
  \begin{figure}[h]
    \pgfplotsset{grid style={dotted,gray}}
    \begin{tikzpicture}
      \begin{axis}[
          width=0.8\textwidth,
          height=0.6\textwidth,
          xtick={1,...,4},
          xmin=1,
          xmax=4,
          ymin=0,
          grid=both,
          legend style={at={(1.35,1)},anchor=north east},
          legend entries={
            \footnotesize{OpenMP},
            \footnotesize{OpenMP SIMD},
            \footnotesize{Sequential SIMD},
            \footnotesize{Sequential}
          },
          xlabel={\small Number of threads},
          ylabel={\small Time (Fraction of sequential time)}
        ]
        %% omp
        \addplot[densely dashed,color=orange,mark=*] coordinates{
          (1,2.1623)
          (2,3.51068)
          (3,3.50279)
          (4,3.7016)
        };
        %% omp simd
        \addplot[densely dashed,color=teal,mark=*] coordinates{
          (1,2.07451)
          (2,3.40727)
          (3,3.56501)
          (4,3.41178)
        };
        %% simd
        \addplot[color=purple,mark=x] coordinates{
          (1,0.837713)
          (2,0.837713)
          (3,0.837713)
          (4,0.837713)
        };
        \addplot[color=orange,mark=x] coordinates{
          (1,1)
          (2,1)
          (3,1)
          (4,1)
        };
      \end{axis}
    \end{tikzpicture}
    \caption{Small scenario}
  \end{figure}
\end{center}
\section{Questions}
\begin{enumerate}[label=\Alph*.]
\item \textbf{What kind of parallelism is exposed with your code
  refactorization?}\\ The parallelism exposed is that of data
  parallelism, where multiple workers access different part of the
  agent and waypoint data simultaneously.
  
\item \textbf{Give a short summary of similarities and differences
  between SIMD and OpenCL.}\\ One of the similarites between OpenCL
  and SIMD is the importance of aligned data to facilitate the many
  moves between memory types. OpenCL offers more flexibility then
  SIMD, as SIMD only supports very specific instructions compared to
  OpenCL's C implementation. The methods used by the two differ as
  well, since SIMD instructions performances multiple operations
  simultaneously while OpenCL performs multiple operations in
  parallel.
  
\item \textbf{Which parallelization has been most beneficial in these
  two labs? Support your case using plotted time measurements.}\\ As
  shown in Figure 1, the mix of using SIMD calls together with OpenMP
  parallelism provides a significant increase in performance over
  every other form of optimization and even at its worst, OpenMP
  outperformed every other implementation tried.

  However, in Figure 2 we see that when using a smaller amount of
  data, the overhead outweighs the performance and slows down the
  execution time significantly. Not pictured in the figure is the
  OpenCL and PThreads implemenations because their performance was
  poor enough under these circumstances to skew the graph.

\item \textbf{What kind of code transformations were required for this
  lab, and why were they needed?}\\ For the lab, we first of all went
  through the codebase, restructuring and making more efficient the
  various function calls and rooting out unused member-variables to
  make it easier for us to find what work was actually being
  done. With this, we were able to write an OpenCL kernel that could
  perform the task imperatively, given a minimum amount of
  information. The vector class had an overhaul where the various
  functions were vectorized to increase performance and lower the
  required work used for normalization and similar efforts.

\item \textbf{Compare the effort required for each of the four
  parallellization techniques. Would it have made a difference if you
  had to build the program from scratch, instead of using given
  code?}\\ Making use of Pthreads and OpenMP required a rather small
  amount of code changes to outperform the sequential method, relying
  more on the number of worker threads than anything else to provide
  performance increase. However, adjusting the code to make good use
  of SIMD instructions and to use OpenCL effectively required a
  substantial amount of re-structuring and indeed for OpenCL the
  previous implementation was largely abandoned altogether and moved
  into a kernel program. If the program had been designed with this in
  mind from the start, it would no doubt have been easier to translate
  the idea into a kernel program.
\end{enumerate}
\section{How to run}
The demo runs with a GUI and using the sequential implementation if no
flag has overwritten the settings. The following flags can be used to
alter the demo and change the implementation for the tick function.
\begin{itemize}[label=,leftmargin=0pt]
\item \textbf{-\--timing-mode} - Without gui.
\item \textbf{-\--pthreads} - Executes the PThreads implementation.
\item \textbf{-\--omp} - Executes the OpenMP implementation.
\item \textbf{-\--opencl} - Executes the OpenCL implementation.
\item \textbf{-\--simd} - Executes the SIMD implementation, can be
  combined with either omp or pthreads.
\item \textbf{-\--threads \textit{number}} - Tells the demo to use
  \textit{number} threads when executing.
\item \textbf{-\--silent} - Does not print to standard output.
\item \textbf{-\--plot} - Stores the timing data to the file
  testdata.txt
\end{itemize}
\section*{Work effort}
Jimmy and Per worked equally with all parts of the lab. Fredrik did not participate.
\end{document}
