\documentclass[a4paper,11pt]{article}
\usepackage[british]{babel}
\usepackage{fullpage}
\usepackage{amsmath,amssymb}
\usepackage{multirow}
\usepackage{caption}
\usepackage{tikz,pgfplots}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\title{\textbf{Low-level Parallel Programming (course 1DL550) \\
    Uppsala University -- Spring 2015 \\
    Report for Lab 2 by Team 14}}
\author{Fredrik Larsson \and Jimmy Holm \and Per Bergqwist}
\date{\today}
\begin{document}
\maketitle
\section{Plot}
\begin{center}
  \pgfplotsset{grid style={dotted,gray}}
  \begin{tikzpicture}
    \begin{axis}[
        width=0.8\textwidth,
        height=0.6\textwidth,
        xtick={2,...,14},
        xmin=2,
        xmax=14,
        ymin=0,
        grid=both,
        legend entries={\small{},\small{}},
        xlabel={\small{}},
        ylabel={\small{}}
      ]
      \addplot coordinates{
      }
      \addplot coordinates{
      }
      \draw (axis cs:2,1) -- (axis cs:14,1);
    \end{axis}
  \end{tikzpicture}
\end{center}

\section{System specification}

\section{Questions}
\begin{enumerate}[label=\Alph*.]
\item \textbf{What kind of parallelism is exposed with your code refactorization?}\\

\item \textbf{Give a short summary of similarities and differences between SIMD and CUDA.}\\

\item \textbf{Which parallelization has been most beneficial in these two labs? Support your case using plotted time measurements.}\\ 

\item \textbf{What kind of code transformations were required for this lab, and why were they needed?}\\

\item \textbf{Compare the effort required for each of the four parallellization techniques. Would it have made a difference if you had to build the program from scratch, instead of using given code?}\\

\end{enumerate}
\section{How to run}
The demo runs with a GUI and using the sequential implementation
if no flag has overwritten the settings. The following flags can be
used to alter the demo and change the implementation for the tick
function.
\begin{itemize}[label=,leftmargin=0pt]
\item \textbf{-\--timing-mode} - Without gui.
\item \textbf{-\--pthread} - Executes the PThread implementation.
\item \textbf{-\--omp} - Executes the OpenMP implementation.
\item \textbf{-\--cude} - Executes the CUDA implementation.
\item \textbf{-\--simd} - Executes the SIMD implementation·
\item \textbf{-\--threads \textit{number}} - Tells the demo to use
  \textit{number} threads when executing.

\item \textbf{-\--silent} - Does not print to standard output.
\item \textbf{-\--plot} - Stores the timing data to the file testdata.txt
\end{itemize}
\end{document}
